On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-03-10 Manuscript/manuscript.tex
structure for section 2

\title{How Large a Sample Size is Needed for Block Bootstrap Confidence
  Intervals
  to Have Desired Coverage Rates?}

\author{Mathew Chandy
%   \href{mailto:mathew.chandy@uconn.edu}
% {\nolinkurl{mathew.chandy@uconn.edu}}\\
  \and Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

@@

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare three variants of block bootstrap
confidence intervals from the literature \citep{diciccio1996bootstrap}
\citep{rice2006mathematical}: a basic percentile interval, a percentile
interval centered around the original estimate, and a bias-corrected and
accelerated ($BC_a$) interval also centered around the original estimate. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

@@

\jy{set up notations for sample; give the algorithm to perform bootstrap
  procedure}

\jy{two subsections: 1) block bootstrap basics; 2) bootstrap CIs. The different
  CIs should each take a paragraph.}

\jy{Needs to distinguish the basic percentile bootstrap and corrected percentile
  bootstrap. Recall that we had trouble covering phi using the basic percentile
  method.}

>>>>

\title{On Sample Size for Block Bootstrap Confidence Intervals 
  to Have Desired Coverage Rates}

\author{Mathew Chandy
%   \href{mailto:mathew.chandy@uconn.edu}
% {\nolinkurl{mathew.chandy@uconn.edu}}\\
  and Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

@@

The goal of this paper is to provide some practical recommendations on
necessary sample size for block bootstrap with dependent data. We consider a
simple situation of a stationary time series, where the parameters of
interests are the mean, standard deviation, and the first-order
autocorrelation coefficient. We compare three variants of block bootstrap
confidence intervals from the literature \citep{diciccio1996bootstrap,
  rice2006mathematical}: a basic percentile interval, a percentile
interval centered around the estimate, and a bias-corrected and
accelerated ($BC_a$) interval also centered around the original estimate. Their
empirical coverage rates at different sample sizes and dependence levels are
compared in a simulation study. The results of this study suggest that
appropriate recovery of temporal dependence parameters is heavily dependent on
the type of interval used.

@@

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
Our goal is to construct a confidence intervals for a parameter $\theta$ in the
data generating model of the series. Suppose that $\hat\theta_n$ is a point
estimator of~$\theta$ based on the observed series. Bootstrap is a powerful
approach to construct confidence intervals. If the observations in the series
were independent, a standard nonparametric bootstrap procedure would draw a
large number~$B$ bootstrap copies of the observed data, and calculate an
estimate $\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. The uncertainty
of $\hat\theta_n$ is then estimated by the empirical uncertainty of the
$\hat\theta_n^{(b)}$'s. When serial dependence is present, the bootstrap
procedure needs to preserve the serial dependence. Block bootstrap was motivated
for this situation.

\subsection{Draw a Block Bootstrap Sample}

\jy{Paragraph: describe how to construct one non-overlapping block bootstrap
  sample.}

\jy{Paragraph: describe how to construct one overlapping block bootstrap.}

\jy{Paragraph: comment on selection block size;
  mention that the two procedures are both valid with similar performance (cite
  references to support the claim).}

\subsection{Construct Confidence Intervals}

Suppose that we have repeated the steps in the last subsection $B$ times, and
that for $b \in \{1, \ldots, B\}$, we have obtained an estimator
$\hat\theta_n^{(b)}$ based on the $b$th bootstrap sample using the same method
that was applied to $\{X_t: t = 1, \ldots, n\}$ to obtain $\hat\theta_n$.
Now the question is, how to construct confidence intervals for $\theta$
using the $B$ bootstrap point estimates
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$.

\jy{Paragraph: bascic percentiles; use the terminologies in the literature.}

\jy{Paragraph: centered.}

\jy{Paragraph: BCa}
